plots for paper

### 2019-10-22 src/plots for paper.Rmd
looking to add contours
fandangled plotting

```{r}
mar <- read.csv("../output//maxent/paper_plots/prob_by_depth/mar_u0.4s_dis_prob_cells.csv", header = TRUE)
mar <- mar[!(mar$Depth =="1151.99" | mar$Depth =="1265.86" | mar$Depth =="1387.38"), ]
mar$Probability <- gsub(">0.9", "0.9 - 1", mar$Probability)
mar$Depth <- as.factor(mar$Depth)
flevelsm <- levels(mar$Depth)
flevelsm <- rev(flevelsm)

jun <- read.csv("../output//maxent/paper_plots/prob_by_depth/jun_u0.4s_dis_prob_cells.csv", header = TRUE)
jun <- jun[!(jun$Depth =="1151.99" | jun$Depth =="1265.86" | jun$Depth =="1387.38"), ]
jun$Probability <- gsub(">0.9", "0.9 - 1", jun$Probability)
jun$Depth <- as.factor(jun$Depth)
flevelsj <- levels(jun$Depth)
flevelsj <- rev(flevelsj)

sep <- read.csv("../output//maxent/paper_plots/prob_by_depth/sep_u0.4s_dis_prob_cells.csv", header = TRUE)
sep <- sep[!(sep$Depth =="1151.99" | sep$Depth =="1265.86" | sep$Depth =="1387.38"), ]
sep$Probability <- gsub(">0.9", "0.9 - 1", sep$Probability)
sep$Depth <- as.factor(sep$Depth)
flevelss <- levels(sep$Depth)
flevelss <- rev(flevelss)

dec <- read.csv("../output//maxent/paper_plots/prob_by_depth/dec_u0.4s_dis_prob_cells.csv", header = TRUE)
dec <- dec[!(dec$Depth =="1151.99" | dec$Depth =="1265.86" | dec$Depth =="1387.38"), ]
dec$Probability <- gsub(">0.9", "0.9 - 1", dec$Probability)
dec$Depth <- as.factor(dec$Depth)
flevelsd <- levels(dec$Depth)
flevelsd <- rev(flevelsd)

probcol <- rev(brewer.pal(7,"RdYlGn"))

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsm, breaks=flevelsm[seq(1,length(flevelsm), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pj <- ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsj, breaks=flevelsj[seq(1,length(flevelsj), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "June") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

ps <- ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelss, breaks=flevelss[seq(1,length(flevelss), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "September") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pd <- ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_manual(values = probcol) + scale_x_discrete(limits = flevelsd, breaks=flevelsd[seq(1,length(flevelsd), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "December") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

# # arrange the four plots in a single row
# prow <- plot_grid(
#   pm + theme(legend.position="none"),
#   pj + theme(legend.position="none"),
#  # ps + theme(legend.position="none"),
# #  pd + theme(legend.position="none"),
#   align = 'vh',
#   #labels = c("A", "B") #, "C", "D"),
#   hjust = -1,
#   nrow = 1
# )
# 
# legend <- get_legend(
#   # create some space to the left of the legend
#   pm + theme(legend.box.margin = margin(0, 0, 0, 12))
# )
# 
# # add the legend to the row we made earlier. Give it one-third of 
# # the width of one plot (via rel_widths).
# t <- plot_grid(prow, legend, rel_widths = c(3, .4))
# 
# t
pm

@@

now MJ suggested to only show some depths (the most commonly predicted ones)

@@

then create an summary map....
```{r high probability map per year 2D representation}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

>>>>

```{r}
mar <- read.csv("../output/maxent/paper_plots/prob_by_depth/mar_u0.4s_dis_prob_cells.csv", header = TRUE)
mar <- mar[!(mar$Depth =="1151.99" | mar$Depth =="1265.86" | mar$Depth =="1387.38"), ]
mar$Probability <- gsub(">0.9", "0.9 - 1", mar$Probability)
mar$Depth <- as.factor(mar$Depth)
flevelsmar <- levels(mar$Depth)
flevelsmar <- rev(flevelsmar)

apr <- read.csv("../output/maxent/paper_plots/prob_by_depth/apr_u0.4s_dis_prob_cells.csv", header = TRUE)
apr <- apr[!(apr$Depth =="1151.99" | apr$Depth =="1265.86" | apr$Depth =="1387.38"), ]
apr$Probability <- gsub(">0.9", "0.9 - 1", apr$Probability)
apr$Depth <- as.factor(apr$Depth)
flevelsapr <- levels(apr$Depth)
flevelsapr <- rev(flevelsapr)

may <- read.csv("../output/maxent/paper_plots/prob_by_depth/may_u0.4s_dis_prob_cells.csv", header = TRUE)
may <- may[!(may$Depth =="1151.99" | may$Depth =="1265.86" | may$Depth =="1387.38"), ]
may$Probability <- gsub(">0.9", "0.9 - 1", may$Probability)
may$Depth <- as.factor(may$Depth)
flevelsmay <- levels(may$Depth)
flevelsmay <- rev(flevelsmay)

jun <- read.csv("../output/maxent/paper_plots/prob_by_depth/jun_u0.4s_dis_prob_cells.csv", header = TRUE)
jun <- jun[!(jun$Depth =="1151.99" | jun$Depth =="1265.86" | jun$Depth =="1387.38"), ]
jun$Probability <- gsub(">0.9", "0.9 - 1", jun$Probability)
jun$Depth <- as.factor(jun$Depth)
flevelsjun <- levels(jun$Depth)
flevelsjun <- rev(flevelsjun)

jul <- read.csv("../output/maxent/paper_plots/prob_by_depth/jul_u0.4s_dis_prob_cells.csv", header = TRUE)
jul <- jul[!(jul$Depth =="1151.99" | jul$Depth =="1265.86" | jul$Depth =="1387.38"), ]
jul$Probability <- gsub(">0.9", "0.9 - 1", jul$Probability)
jul$Depth <- as.factor(jul$Depth)
flevelsjul <- levels(jul$Depth)
flevelsjul <- rev(flevelsjul)

aug <- read.csv("../output/maxent/paper_plots/prob_by_depth/aug_u0.4s_dis_prob_cells.csv", header = TRUE)
aug <- aug[!(aug$Depth =="1151.99" | aug$Depth =="1265.86" | aug$Depth =="1387.38"), ]
aug$Probability <- gsub(">0.9", "0.9 - 1", aug$Probability)
aug$Depth <- as.factor(aug$Depth)
flevelsaug <- levels(aug$Depth)
flevelsaug <- rev(flevelsaug)

sep <- read.csv("../output/maxent/paper_plots/prob_by_depth/sep_u0.4s_dis_prob_cells.csv", header = TRUE)
sep <- sep[!(sep$Depth =="1151.99" | sep$Depth =="1265.86" | sep$Depth =="1387.38"), ]
sep$Probability <- gsub(">0.9", "0.9 - 1", sep$Probability)
sep$Depth <- as.factor(sep$Depth)
flevelssep <- levels(sep$Depth)
flevelssep <- rev(flevelssep)

oct <- read.csv("../output/maxent/paper_plots/prob_by_depth/oct_u0.4s_dis_prob_cells.csv", header = TRUE)
oct <- oct[!(oct$Depth =="1151.99" | oct$Depth =="1265.86" | oct$Depth =="1387.38"), ]
oct$Probability <- gsub(">0.9", "0.9 - 1", oct$Probability)
oct$Depth <- as.factor(oct$Depth)
flevelsoct <- levels(oct$Depth)
flevelsoct <- rev(flevelsoct)

nov <- read.csv("../output/maxent/paper_plots/prob_by_depth/nov_u0.4s_dis_prob_cells.csv", header = TRUE)
nov <- nov[!(nov$Depth =="1151.99" | nov$Depth =="1265.86" | nov$Depth =="1387.38"), ]
nov$Probability <- gsub(">0.9", "0.9 - 1", nov$Probability)
nov$Depth <- as.factor(nov$Depth)
flevelsnov <- levels(nov$Depth)
flevelsnov <- rev(flevelsnov)

dec <- read.csv("../output/maxent/paper_plots/prob_by_depth/dec_u0.4s_dis_prob_cells.csv", header = TRUE)
dec <- dec[!(dec$Depth =="1151.99" | dec$Depth =="1265.86" | dec$Depth =="1387.38"), ]
dec$Probability <- gsub(">0.9", "0.9 - 1", dec$Probability)
dec$Depth <- as.factor(dec$Depth)
flevelsdec <- levels(dec$Depth)
flevelsdec <- rev(flevelsdec)

probcol <- viridisTheme(option = inferno, rev(10))

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsmar, breaks=flevelsmar[seq(1,length(flevelsmar), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pa <- ggplot(apr, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsapr, breaks=flevelsapr[seq(1,length(flevelsapr), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "April") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pma <- ggplot(may, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="plasma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsmay, breaks=flevelsmay[seq(1,length(flevelsmay), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "May") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pj <- ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option="inferno", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsjun, breaks=flevelsjun[seq(1,length(flevelsjun), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "June") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pju <- ggplot(jul, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsjul, breaks=flevelsjul[seq(1,length(flevelsjul), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "July") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pau <- ggplot(aug, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsaug, breaks=flevelsaug[seq(1,length(flevelsaug), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "August") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

ps <- ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelssep, breaks=flevelssep[seq(1,length(flevelssep), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "September") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

po <- ggplot(oct, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="plasma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsoct, breaks=flevelsoct[seq(1,length(flevelsoct), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "October") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pn <- ggplot(nov, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsnov, breaks=flevelsnov[seq(1,length(flevelsnov), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "November") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pd <- ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option = "inferno", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsdec, breaks=flevelsdec[seq(1,length(flevelsdec), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "December") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pm
pa
pma
pj
pju
pa
ps
po
pn
pd

@@

and repeat without the 0.4 cut....

```{r}
mar <- read.csv("../output/maxent/paper_plots/prob_by_depth/mar_dis_prob_cells.csv", header = TRUE)
mar <- mar[!(mar$Depth =="1151.99" | mar$Depth =="1265.86" | mar$Depth =="1387.38"), ]
mar$Probability <- gsub(">0.9", "0.9 - 1", mar$Probability)
mar$Depth <- as.factor(mar$Depth)
flevelsmar <- levels(mar$Depth)
flevelsmar <- rev(flevelsmar)

apr <- read.csv("../output/maxent/paper_plots/prob_by_depth/apr_dis_prob_cells.csv", header = TRUE)
apr <- apr[!(apr$Depth =="1151.99" | apr$Depth =="1265.86" | apr$Depth =="1387.38"), ]
apr$Probability <- gsub(">0.9", "0.9 - 1", apr$Probability)
apr$Depth <- as.factor(apr$Depth)
flevelsapr <- levels(apr$Depth)
flevelsapr <- rev(flevelsapr)

may <- read.csv("../output/maxent/paper_plots/prob_by_depth/may_dis_prob_cells.csv", header = TRUE)
may <- may[!(may$Depth =="1151.99" | may$Depth =="1265.86" | may$Depth =="1387.38"), ]
may$Probability <- gsub(">0.9", "0.9 - 1", may$Probability)
may$Depth <- as.factor(may$Depth)
flevelsmay <- levels(may$Depth)
flevelsmay <- rev(flevelsmay)

jun <- read.csv("../output/maxent/paper_plots/prob_by_depth/jun_dis_prob_cells.csv", header = TRUE)
jun <- jun[!(jun$Depth =="1151.99" | jun$Depth =="1265.86" | jun$Depth =="1387.38"), ]
jun$Probability <- gsub(">0.9", "0.9 - 1", jun$Probability)
jun$Depth <- as.factor(jun$Depth)
flevelsjun <- levels(jun$Depth)
flevelsjun <- rev(flevelsjun)

jul <- read.csv("../output/maxent/paper_plots/prob_by_depth/jul_dis_prob_cells.csv", header = TRUE)
jul <- jul[!(jul$Depth =="1151.99" | jul$Depth =="1265.86" | jul$Depth =="1387.38"), ]
jul$Probability <- gsub(">0.9", "0.9 - 1", jul$Probability)
jul$Depth <- as.factor(jul$Depth)
flevelsjul <- levels(jul$Depth)
flevelsjul <- rev(flevelsjul)

aug <- read.csv("../output/maxent/paper_plots/prob_by_depth/aug_dis_prob_cells.csv", header = TRUE)
aug <- aug[!(aug$Depth =="1151.99" | aug$Depth =="1265.86" | aug$Depth =="1387.38"), ]
aug$Probability <- gsub(">0.9", "0.9 - 1", aug$Probability)
aug$Depth <- as.factor(aug$Depth)
flevelsaug <- levels(aug$Depth)
flevelsaug <- rev(flevelsaug)

sep <- read.csv("../output/maxent/paper_plots/prob_by_depth/sep_dis_prob_cells.csv", header = TRUE)
sep <- sep[!(sep$Depth =="1151.99" | sep$Depth =="1265.86" | sep$Depth =="1387.38"), ]
sep$Probability <- gsub(">0.9", "0.9 - 1", sep$Probability)
sep$Depth <- as.factor(sep$Depth)
flevelssep <- levels(sep$Depth)
flevelssep <- rev(flevelssep)

oct <- read.csv("../output/maxent/paper_plots/prob_by_depth/oct_dis_prob_cells.csv", header = TRUE)
oct <- oct[!(oct$Depth =="1151.99" | oct$Depth =="1265.86" | oct$Depth =="1387.38"), ]
oct$Probability <- gsub(">0.9", "0.9 - 1", oct$Probability)
oct$Depth <- as.factor(oct$Depth)
flevelsoct <- levels(oct$Depth)
flevelsoct <- rev(flevelsoct)

nov <- read.csv("../output/maxent/paper_plots/prob_by_depth/nov_dis_prob_cells.csv", header = TRUE)
nov <- nov[!(nov$Depth =="1151.99" | nov$Depth =="1265.86" | nov$Depth =="1387.38"), ]
nov$Probability <- gsub(">0.9", "0.9 - 1", nov$Probability)
nov$Depth <- as.factor(nov$Depth)
flevelsnov <- levels(nov$Depth)
flevelsnov <- rev(flevelsnov)

dec <- read.csv("../output/maxent/paper_plots/prob_by_depth/dec_dis_prob_cells.csv", header = TRUE)
dec <- dec[!(dec$Depth =="1151.99" | dec$Depth =="1265.86" | dec$Depth =="1387.38"), ]
dec$Probability <- gsub(">0.9", "0.9 - 1", dec$Probability)
dec$Depth <- as.factor(dec$Depth)
flevelsdec <- levels(dec$Depth)
flevelsdec <- rev(flevelsdec)

probcol <- viridisTheme(option = inferno, rev(10))

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsmar, breaks=flevelsmar[seq(1,length(flevelsmar), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pa <- ggplot(apr, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsapr, breaks=flevelsapr[seq(1,length(flevelsapr), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "April") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pma <- ggplot(may, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="plasma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsmay, breaks=flevelsmay[seq(1,length(flevelsmay), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "May") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pj <- ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option="inferno", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsjun, breaks=flevelsjun[seq(1,length(flevelsjun), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "June") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pju <- ggplot(jul, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsjul, breaks=flevelsjul[seq(1,length(flevelsjul), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "July") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pau <- ggplot(aug, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsaug, breaks=flevelsaug[seq(1,length(flevelsaug), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "August") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

ps <- ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelssep, breaks=flevelssep[seq(1,length(flevelssep), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "September") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

po <- ggplot(oct, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="plasma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsoct, breaks=flevelsoct[seq(1,length(flevelsoct), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "October") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pn <- ggplot(nov, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="viridis", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsnov, breaks=flevelsnov[seq(1,length(flevelsnov), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "November") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pd <- ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option = "inferno", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsdec, breaks=flevelsdec[seq(1,length(flevelsdec), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "December") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0))

pm
pa
pma
pj
pju
pa
ps
po
pn
pd

now MJ suggested to only show some depths (the most commonly predicted ones) NOTE DECIDED MAYBE NOT GOOD BECAUSE OF NEW GRAPHIC PLUS DEPTH CHANGES

@@

then create an summary map....
```{r >0.5 prob monthly 2D representation}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

xxxx
```{r}
library(raster)
library(rgdal)
library(rasterVis)
library(colorspace)

aea <- raster("../output/env/aea.tif") #the correct CRS
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")
ss <- raster::intersect(s, mcp)  #trim land file to mcp

maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
maplst2 <- list.files("../output/maxent/predictions/sep", pattern = "^avg_clog.*.asc", full.names = TRUE)
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

pras6 <- raster(maplst[37])
pras180 <- raster(maplst[14])
pras370 <- raster(maplst[28])
pras697 <- raster(maplst[41])
p2ras6 <- raster(maplst2[37])
p2ras180 <- raster(maplst2[14])
p2ras370 <- raster(maplst2[28])
p2ras697 <- raster(maplst2[41])
crs(pras6) <- apr
crs(pras180) <- apr
crs(pras370) <- apr
crs(pras697) <- apr
crs(p2ras6) <- apr
crs(p2ras180) <- apr
crs(p2ras370) <- apr
crs(p2ras697) <- apr
ascname6 <- names(pras6)
ascname180 <- names(pras180)
ascname370 <- names(pras370)
ascname697 <- names(pras697)
a2scname6 <- names(p2ras6)
a2scname180 <- names(p2ras180)
a2scname370 <- names(p2ras370)
a2scname697 <- names(p2ras697)

# pstack <- stack(pras6, pras180, pras370, pras697) #stack the layers
# 
# pras1 <- raster(maplst[1])
# pras2 <- raster(maplst[2])
# pras3 <- raster(maplst[3])
# pras4 <- raster(maplst[4])
# crs(pras1) <- apr
# crs(pras2) <- apr
# crs(pras3) <- apr
# crs(pras4) <- apr

pstack <- stack(pras6, pras180, pras370, pras697, p2ras6, p2ras180, p2ras370, p2ras697) #stack the layers

cls <- c("6m", "180m", "370m", "697m")
rws <- c("May", "Sep")
mapTheme <- rasterTheme(region = rev(brewer.pal(10,"RdYlGn")))
my.at <- seq(0, 1, by = 0.1)

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(4, 2), names.attr = c("6m", "180m", "370m", "697m", "", "", "", ""), margin = FALSE)
p + layer(sp.polygons(s, fill = "black")) + layer (sp.polygons(outsidemcp, fill = redtrans, col = NA))

#dev.copy(png, (paste0("../output/maxent/predictions/testplots/rasterVis.png")), width = 1920,height = 1080)
#dev.off() # stops automatic saving of the plot to a png))

#coloured histograms

```{r}
mar <- raster("../output/maxent/predictions/mar/avg_cloglog_97.0413.asc")
#apr <- raster("../output/maxent/predictions/apr/avg_cloglog_97.0413.asc")

mardf <- as.data.frame(mar) #convert raster to dataframe
mardf <- na.omit(mardf) #remove all the land 
for (i in 1:nrow(mardf)){
  if (mardf$avg_cloglog_97.0413[i] <=0.1){
    mardf$bin[i] <- 1
  } else if (mardf$avg_cloglog_97.0413[i] >0.1 & mardf$avg_cloglog_97.0413[i] <= 0.2){
      mardf$bin[i] <- 2
  } else if (mardf$avg_cloglog_97.0413[i] >0.2 & mardf$avg_cloglog_97.0413[i] <= 0.3){
      mardf$bin[i] <- 3
  } else if (mardf$avg_cloglog_97.0413[i] >0.3 & mardf$avg_cloglog_97.0413[i] <= 0.4){
      mardf$bin[i] <- 4
  } else if (mardf$avg_cloglog_97.0413[i] >0.4 & mardf$avg_cloglog_97.0413[i] <= 0.5){
      mardf$bin[i] <- 5
  } else if (mardf$avg_cloglog_97.0413[i] >0.5 & mardf$avg_cloglog_97.0413[i] <= 0.6){
      mardf$bin[i] <- 6
  } else if (mardf$avg_cloglog_97.0413[i] >0.6 & mardf$avg_cloglog_97.0413[i] <= 0.7){
      mardf$bin[i] <- 7
  } else if (mardf$avg_cloglog_97.0413[i] >0.7 & mardf$avg_cloglog_97.0413[i] <= 0.8){
      mardf$bin[i] <- 8
  } else if (mardf$avg_cloglog_97.0413[i] >0.8 & mardf$avg_cloglog_97.0413[i] <= 0.9){
      mardf$bin[i] <- 9
  } else if (mardf$avg_cloglog_97.0413[i] >0.9){
      mardf$bin[i] <- 10
  }
}

mardf$bin <- as.factor(mardf$bin)

brk <- seq(0.1, 1, 0.1) #bins you want
brkl <- as.character(brk)

p <- ggplot(mardf, aes(x = avg_cloglog_97.0413, fill = bin))+ geom_histogram(breaks = brk) + theme_classic() + scale_fill_viridis_d(option = "inferno", direction = -1) + theme(legend.position = "none", plot.title = element_blank(), axis.title.x = element_blank(), axis.title.y = element_blank()) + scale_x_continuous(breaks=seq(0,1,0.1))
png("../output/maxent/paper_plots/histogram_mar_97.png", height = 1024, width = 1024)
p
dev.off()

# variable maps
- temp
- chl 
- o2
- sal
- 4 different months
- relationship of variables to each other
- pick a depth (say the 11.7737 m)

months are mar, jun, sep, dec
pick 3 diff years say 1998, 2006, 2013

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")
ss <- raster::intersect(s, mcp)  #trim land file to mcp

yrlst <- c("1998", "2006", "2013")
mthlst <- c("03", "06", "09", "12")
varlst <- c("temp", "salinity", "o2")

for (y in 1:length(yrlst)){
  yr <- yrlst[y]
  fdr <- paste0("../data/env/ascii/ascii", yr, "/")
  for (m in 1:length(mthlst)){
    mt <- mthlst[m]
    for (v in 1:length(varlst)){
      var <- varlst[v]
      ras <- raster(paste0(fdr, yr, "_", mt, "_", var, ".nc_11.7737.asc"))
      lyrnm <- names(ras)
      crs(ras) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      ras <- projectRaster(ras, aea)
      ras <- raster::mask(ras, mcp)

      p <- levelplot(ras, margin=FALSE, colorkey=list(space='bottom', axis.line=list(col='black')), par.settings=list(axis.line=list(col='transparent')), scales=list(draw=FALSE), col.regions=colorRampPalette(blue2red(20))) + layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))

      png(paste0("../output/maxent/paper_plots/", lyrnm, ".png"), height = 1024, width = 1024)
      print(p)
      dev.off()
    }
  }
}

#chl is done seperately as it is surface

yrlst <- c("1998", "2006", "2013")
mthlst <- c("03", "06", "09", "12")
varlst <- c("chl")

for (y in 1:length(yrlst)){
  yr <- yrlst[y]
  fdr <- paste0("../data/env/ascii/ascii", yr, "/")
  for (m in 1:length(mthlst)){
    mt <- mthlst[m]
    for (v in 1:length(varlst)){
      var <- varlst[v]
      ras <- raster(paste0(fdr, yr, "_", mt, "_", var, ".nc_0.50576.asc"))
      lyrnm <- names(ras)
      crs(ras) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      ras <- projectRaster(ras, aea)
      ras <- raster::mask(ras, mcp)

      p <- levelplot(ras, margin=FALSE, colorkey=list(space='bottom', axis.line=list(col='black')), par.settings=list(axis.line=list(col='transparent')), scales=list(draw=FALSE), col.regions=colorRampPalette(blue2red(20))) + layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))

      png(paste0("../output/maxent/paper_plots/", lyrnm, ".png"), height = 1024, width = 1024)
      print(p)
      dev.off()
    }
  }
}
```
